Globally-centered autocovariances in MCMC

### 2020-07-22 Paper/main.tex
Modified the plots for GaussianMix a little.

\usepackage{amssymb,amsthm,amsmath}
\usepackage{commath}
\usepackage{enumerate,xcolor}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{caption,setspace}
\usepackage{subcaption}
\DeclareMathOperator{\Tr}{Tr}
\newcommand{\dd}[1]{\mathrm{d}#1}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\B}{\mathcal{B}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{comment}
\usepackage[linesnumbered, ruled]{algorithm2e}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
\allowdisplaybreaks
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

@@

Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process. Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones. Therefore, it becomes imperative for an MCMC pG-titioner to have an idea about underlying dependence structure in the Markov chains. Autocovariance function (ACF) chaG-terizes this dependence for a stationary Markov chain. Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e. (1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$. Then, the autocovariance function at lag-$k$ is defined as

\[
    \Gamma(k) = Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
\]

>>>>

\usepackage{amssymb,amsthm,amsmath}
\usepackage{commath}
\usepackage{enumerate,xcolor}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{caption,setspace}
\usepackage{subcaption}
\DeclareMathOperator{\Tr}{Tr}
\newcommand{\dd}[1]{\mathrm{d}#1}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\Cov}{\text{Cov}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\B}{\mathcal{B}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{comment}
\usepackage[linesnumbered, ruled]{algorithm2e}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
\allowdisplaybreaks
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

@@

Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process. Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones. Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains. Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain. Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e. (1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$. Then, the autocovariance function at lag-$k$ is defined as

\[
    \Gamma(k) = \Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
\]
